---
title: "R programming Quiz 1"
author: "Jiaoping"
date: "June 6, 2015"
output: html_document
---
Question 11: Load dataset into Rstudio 
```{r,cache=TRUE}
quizdata<-read.csv("hw1_data-2.csv")
```

Question 12: extract the first 2 rows of the data frame
```{r}
quizdata[1:2,]
```

Question 13: How many observations are there? 
```{r}
nrow(quizdata)
```

Question 14: Extract the last 2 rows of the data frame
```{r}
quizdata[152:153,]
```
Question 15: Find the value of Ozone in the 47th row.
```{r}
quizdata[47,1]
```
Quesiton 16: How many missing values are there in Ozone?
```{r}
Ozone<-quizdata$Ozone
logic<-is.na(Ozone)
Ozone[logic]
```
Quesiton 17: calculate the mean of column Ozone excluding the NA
```{r}
mean(Ozone[!logic])
```
Quesiton 18: extact the subset of rows of the dataframe where Ozone value are above 31 and  Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
logic2<-complete.cases(quizdata)
newdata<-quizdata[logic2,]
newdata2<-newdata[newdata$Ozone >31 & newdata$Temp > 90, ]
mean(newdata2 $Solar.R)
```
Question 19: Find the mean of "Temp" when "Month" is equal to 6.
```{r}
newdata3<- quizdata[quizdata$ Month == 6, ]
mean(newdata3$Temp)
```
Question 20: Find the max zone value in the month of May.
```{r}
newdata4<-newdata[newdata$Month==5, ]
max(newdata4$Ozone)
```

